<!--pandoc
t: html
default-image-extension: png
template: templates/html.template
toc-depth: 4
toc:

t: latex
s:
S:
latex-engine: xelatex
template: templates/latex.template
default-image-extension: pdf
toc-depth: 4
toc:
-->

```{r echo=FALSE, cache=FALSE, results="hide"}
opts_chunk$set(cache=TRUE, fig.cap='', dev=c('png', 'pdf'), fig.width=6,
  fig.height=4)
opts_knit$set('upload.fun' = function(x) sub("\\.[[:alnum:]]*$", "", x) )
opts_chunk$set(cache.path="cache/04/")
```
# Temporal Selection Gradients

```{r t_g_data, cache=FALSE}
library(pander)
set.alignment('right', row.names = 'left')
library(MCMCglmm)
library(arm)
library(dplyr)
library(ggplot2)
library(grid)

# Load Data
load("data/analyses_data/fit_raneff_data.RData")
fit_raneff_data$Year <- as.character(fit_raneff_data$Year)
```

##Does 'Year' significantly improve models of selection?
The significance of interaction terms between Year and the behavioral traits on fitness.

```{r Test_Year}
# GLMMs to test whether selection fluctuates across years.
library(lme4)
# Models with interactions between year and the behavioral traits
fit_raneff_data_blup <- filter(fit_raneff_data, type == "blup")

fit_raneff_data_blup %>%
  group_by(Grid, Year, add = FALSE) %>%
  summarise(n(), var(ars_all))
# grid_years with no variation in fitness need to be removed
fit_raneff_data_blup <- filter(fit_raneff_data_blup,
  !(grid_year %in% c("KL2003", "SU2008")))

# Need to also remove Grid Years with very low sample sizes.
fit_raneff_data_blup %>%
  group_by(Grid, Year, add = FALSE) %>%
  summarise(n(), var(ars_all))
fit_raneff_data_blup <- filter(fit_raneff_data_blup,
  !(grid_year %in% c("KL2004")))

fit_raneff_data_blup$oID <- 1:nrow(fit_raneff_data_blup)
fit_raneff_data_blup <- droplevels(fit_raneff_data_blup)

ars_year <- glmer(ars_all ~ Year + Grid + activity_s + activity_s:Year +
  aggression_s + aggression_s:Year + docility_s + docility_s:Year +
  (1|ID) + (1|oID), data = fit_raneff_data_blup, family = poisson, 
  control=glmerControl(optimizer="bobyqa"))

save(ars_year, file = "data/analyses_data/ars_year.RData")
```

```{r Temporal, results='asis'}
load("data/analyses_data/ars_year.RData")
# Test fit of models. Does the addition of year:traits improve the fit?
library(car)
library(lme4)
aod <- Anova(ars_year, type = 2)
aod <- data.frame(aod)
aod$Chisq <- round(aod$Chisq ,digits = 2)

# Function to convert small p-values into 'P < X'
p.format <- function(x){ 
	out <- signif(x, digits = 2)
  out[x < 0.005]  <- "< 0.005"
	out[x < 0.001]  <- "< 0.001"
	out[x < 0.0001] <- "< 0.0001"
	return(out)
}
# Format p values
aod[ ,3] <- p.format(aod[ ,3])
row.names(aod) <- c("Year", "Grid", "Activity", "Aggression", "Docility",
  "Year x Activity", "Year x Aggression", "Year x Docility")
pandoc.table(aod, caption = 
  "The effect of year on selection for female behavioral traits through annual
reproductive success. Significance was calculated with Wald chisq tests from
a type II analysis of deviance. GLMMs were fitted with identity as a random
effect and assumed a Poisson error distribution.")
```

## Accounting for random effect uncertainty
### Calculate selection gradients
Calculate selection coefficients for each of the 1000 samples of the posterior distribution of random effects.

```{r sel_grad_mcmc_post}
# Function to get posterior distribution of selection gradients
x <- fit_raneff_data %>% filter(type == "raneff" & Year == 2003 & itt == 1)
seCoefMCMC <- function(x){
  mod <- lm(rel_ars ~ aggression + activity + docility, data = x)
  mod_sd <-  lm(rel_ars ~ aggression_sy + activity_sy + docility_sy, data = x)
  res <- c(as.list(coef(mod)[-1]), as.list(coef(mod_sd)[-1]))
  res$Year <- x$Year[1]
  res$itt <- x$itt[1]
  return(data.frame(res, stringsAsFactors = FALSE))
}

start_time <- Sys.time()
sel_grads_mcmc_post <- fit_raneff_data %>%
  filter(type == "raneff") %>%
  group_by(itt, Year, add = FALSE) %>%
  do(seCoefMCMC(.))
print(paste("Approx. run time: ", format(Sys.time() - start_time)))

save(sel_grads_mcmc_post,
  file = "data/analyses_data/sel_grads_mcmc_post.RData")
```

```{r get_creds}
load("data/analyses_data/sel_grads_mcmc_post.RData")
x <- sel_grads_mcmc_post %>% filter(Year == "2003")
getCred <- function(x, sig = 0.05){
  require(MCMCglmm)
  mcmc_data <- x %>% ungroup() %>% select(aggression, activity, docility,
    aggression_sy, activity_sy, docility_sy) %>% mcmc(.)
  pm  <- posterior.mode(mcmc_data)
  int <- HPDinterval(mcmc_data, prob = 1 - sig)
  tbl_df(data.frame(
    Year      = x$Year[1],
    variable  = c("Aggression", "Activity", "Docility", "Aggression", 
    "Activity", "Docility"),
     standardization = c("None", "None", "None", "SD", "SD", "SD"),
    post_mode = pm,
    lower     = int[ ,"lower"],
    upper     = int[ ,"upper"],
    stringsAsFactors = FALSE
    ))
}

getCred(sel_grads_mcmc_post %>% filter(Year == "2004"))

sel_grads_mcmc <- sel_grads_mcmc_post %>%
  group_by(Year, add = FALSE) %>%
  do(getCred(x = ., sig = 0.05))

sel_grads_mcmc$upper_sig_star <- ""
sel_grads_mcmc$lower_sig_star <- ""
sel_grads_mcmc$upper_sig_star[sel_grads_mcmc$post_mode > 0 &
  sel_grads_mcmc$lower > 0] <- "*"
sel_grads_mcmc$lower_sig_star[sel_grads_mcmc$post_mode < 0 &
  sel_grads_mcmc$upper < 0] <- "*"

save(sel_grads_mcmc, sel_grads_mcmc_post, getCred,
  file = "data/analyses_data/sel_grads_mcmc.RData")
```

```{r format_sel_grads_mcmc, results='asis'}
load("data/analyses_data/sel_grads_mcmc.RData")

N <- fit_raneff_data %>%
  filter(type == "blup") %>%
  group_by(Year, add = FALSE) %>%
  summarise(n(), doc_mean = mean(docility, na.rm = TRUE))

# Format for table
sgt <- sel_grads_mcmc
sgt$sig_star <- ""
sgt$sig_star[sgt$post_mode > 0 & sgt$lower > 0] <- "*"
sgt$sig_star[sgt$post_mode < 0 & sgt$upper < 0] <- "*"
sgt$post_mode <- format(round(sgt$post_mode, digits = 2), digits = 1,
  nsmall = 2)
sgt$lower     <- format(round(sgt$lower,     digits = 2), digits = 1,
  nsmall = 2)
sgt$upper     <- format(round(sgt$upper,     digits = 2), digits = 1,
  nsmall = 2)
sgt$coef      <- paste(sgt$post_mode, " (", sgt$lower, " to ", sgt$upper,")",
  sgt$sig_star, sep = '')

sgt_agg <- filter(sgt, variable == "Aggression", standardization == "None")
sgt_act <- filter(sgt, variable == "Activity",   standardization == "None")
sgt_doc <- filter(sgt, variable == "Docility",   standardization == "None")

sgt_agg_sd <- filter(sgt, variable == "Aggression", standardization == "SD")
sgt_act_sd <- filter(sgt, variable == "Activity",   standardization == "SD")
sgt_doc_sd <- filter(sgt, variable == "Docility",   standardization == "SD")


doc_post_mode <- sel_grads_mcmc %>% filter(standardization == "None" & variable == "Docility") 
doc_post_mode$post_mode_m <- doc_post_mode$post_mode * N$doc_mean
doc_post_mode$post_mode_m <- format(round(doc_post_mode$post_mode_m, digits = 2), digits = 1, nsmall = 2)

pandoc.table(
  data.frame(Year = N$Year, N = N[ ,2], Aggression = sgt_agg$coef,
    Acitivity = sgt_act$coef, Docility = sgt_doc$coef
  ),
  caption = "Variance standardized selection gradients (accounting for behavioural uncertainty)."
  )

pandoc.table(
  data.frame(Year = N$Year, N = N[ ,2], mean_trait = N$doc_mean, Docility = doc_post_mode$post_mode_m
  ),
  caption = "Mean standardized selection gradients (accounting for behavioural uncertainty)."
  )

pandoc.table(
  data.frame(Year = N$Year, N = N[ ,2], Aggression = sgt_ns_agg$coef,
    Acitivity = sgt_ns_act$coef, Docility = sgt_ns_doc$coef
  ),
  caption = "Non-standardized selection gradients (accounting for behavioural uncertainty)."
  )
```

### Plots
```{r sel_grads_mcmc_plot_SD, fig.cap="SD Standardized Selection Gradients"}
load("data/analyses_data/sel_grads_mcmc_post.RData")
library(ggplot2)
library(dplyr)

sel_grads_mcmc <- sel_grads_mcmc_post %>%
  group_by(Year, add = FALSE) %>% do(getCred(x = ., sig = 0.05))

sel_grads_mcmc$upper_sig_star <- ""
sel_grads_mcmc$lower_sig_star <- ""
sel_grads_mcmc$upper_sig_star[sel_grads_mcmc$post_mode > 0 &
  sel_grads_mcmc$lower > 0] <- "*"
sel_grads_mcmc$lower_sig_star[sel_grads_mcmc$post_mode < 0 &
  sel_grads_mcmc$upper < 0] <- "*"

p <- ggplot(data = filter(sel_grads_mcmc, standardization == "SD"),
  aes(x = Year, y = post_mode, group = variable))
p <- p + geom_hline(yintercept = 0, size = 0.25) # Line at y = 0
p <- p + geom_errorbar(aes(ymax = upper, ymin = lower),
  position = position_dodge(width = 0.5), width = 0.4, size = 0.4)
# Houle data percentiles
p <- p + geom_hline(yintercept = c(0.2975, -0.2975), linetype = 2, size = 0.4)
p <- p + geom_point(aes(shape = variable, fill = variable),
  position = position_dodge(width = 0.5), size = 3)
p <- p + scale_shape_manual(name = "B", values = c(24, 21, 22))
p <- p + scale_fill_manual(name = "B", values = c("white", "black", "white"))
p <- p + scale_color_manual(name = "B", values = c("black", "black", "black"))
p <- p + xlab("Year") 
p <- p + ylab("Posterior Mode ± 0.95 Credible Interval")
p <- p + theme_bw(base_size = 10)
p <- p + theme(legend.position = c(0.92, 0.86),
  legend.background = element_blank(), legend.key.size = unit(0.4, "cm"))
p <- p + theme(legend.title = element_text(family = "Helvetica",
                                 face = "plain", size = 18))
p <- p + theme(legend.key = element_blank())
p <- p + theme(strip.background = element_blank())
p <- p + theme(panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())
p <- p + theme(panel.border = element_blank())
p <- p + theme(axis.line = element_line(color = "black"))
p <- p + geom_text(aes(x = Year, y = upper, group = variable,
  label = upper_sig_star), vjust = -0.3,
  position = position_dodge(width = 0.5), size = 5)
p <- p + geom_text(aes(x = Year, y = lower, group = variable,
  label = lower_sig_star), vjust = 1.3,
  position = position_dodge(width = 0.5), size = 5)
p_sel_grad_MCMC <- p + ylim(c(-1.1,1.4))

pdf(file = "figure/sel_grads_mcmc_plot_SD.pdf", width = 4.33, height = 3)
p_sel_grad_MCMC
dev.off()
p_sel_grad_MCMC
```

```{r sel_grads_mcmc_plot_NoS, fig.cap="Non-standardized Selection Gradients"}
load("data/analyses_data/sel_grads_mcmc_post.RData")
library(ggplot2)
library(dplyr)

sel_grads_mcmc <- sel_grads_mcmc_post %>%
  group_by(Year, add = FALSE) %>% do(getCred(x = ., sig = 0.05))

sel_grads_mcmc$upper_sig_star <- ""
sel_grads_mcmc$lower_sig_star <- ""
sel_grads_mcmc$upper_sig_star[sel_grads_mcmc$post_mode > 0 &
  sel_grads_mcmc$lower > 0] <- "*"
sel_grads_mcmc$lower_sig_star[sel_grads_mcmc$post_mode < 0 &
  sel_grads_mcmc$upper < 0] <- "*"

p <- ggplot(data = filter(sel_grads_mcmc, standardization == "None"),
  aes(x = Year, y = post_mode, group = variable)
)
p <- p + geom_hline(yintercept = 0, size = 0.25) # Line at y = 0
p <- p + geom_errorbar(aes(ymax = upper, ymin = lower),
  position = position_dodge(width = 0.5), width = 0.4, size = 0.4)
# Houle data percentiles
p <- p + geom_hline(yintercept = c(0.2975, -0.2975), linetype = 2, size = 0.4)
p <- p + geom_point(aes(shape = variable, fill = variable),
  position = position_dodge(width = 0.5), size = 3)
p <- p + scale_shape_manual(name = "B", values = c(24, 21, 22))
p <- p + scale_fill_manual(name = "B", values = c("white", "black", "white"))
p <- p + scale_color_manual(name = "B", values = c("black", "black", "black"))
p <- p + xlab("Year") 
p <- p + ylab("Posterior Mode ± 0.95 Credible Interval")
p <- p + theme_bw(base_size = 10)
p <- p + theme(legend.position = c(0.92, 0.86),
  legend.background = element_blank(), legend.key.size = unit(0.4, "cm"))
p <- p + theme(legend.title = element_text(family = "Helvetica",
                                 face = "plain", size = 18))
p <- p + theme(legend.key = element_blank())
p <- p + theme(strip.background = element_blank())
p <- p + theme(panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())
p <- p + theme(panel.border = element_blank())
p <- p + theme(axis.line = element_line(color = "black"))
p <- p + geom_text(aes(x = Year, y = upper, group = variable,
  label = upper_sig_star), vjust = -0.3,
  position = position_dodge(width = 0.5), size = 5)
p <- p + geom_text(aes(x = Year, y = lower, group = variable,
  label = lower_sig_star), vjust = 1.3,
  position = position_dodge(width = 0.5), size = 5)
p_sel_grad_MCMC <- p + ylim(c(-1.1,1.4))

pdf(file = "figure/sel_grads_mcmc_plot_none.pdf", width = 4.33, height = 3)
p_sel_grad_MCMC
dev.off()
p_sel_grad_MCMC
```

### Correlations

```{r sg_cors_mcmc, fig.width=5, fig.height=5}
sel_grads_mcmc_flat <- data.frame(
  Aggression = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Aggression")$post_mode,
  Agg_upper  = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Aggression")$upper,
  Agg_lower  = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Aggression")$lower,
  Activity   = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Activity")$post_mode,
  Act_upper  = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Activity")$upper,
  Act_lower  = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Activity")$lower,
  Docility   = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Docility")$post_mode,
  Doc_upper  = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Docility")$upper,
  Doc_lower  = filter(sel_grads_mcmc, standardization == "SD",
   variable == "Docility")$lower
)

cor.behav <- function(x, y){
  ct <- cor.test(x, y)
  out <- data.frame(est = ct$estimate, lower = ct$conf.int[1],
    upper = ct$conf.int[2], stringsAsFactors = FALSE)
  out <- round(out, digits = 2)
  out$print <- paste(out$est, " (", out$lower, ", ", out$upper, ")", sep = "")
}

cor_agg_act <- cor.behav(sel_grads_mcmc_flat$Aggression, 
  sel_grads_mcmc_flat$Activity)
cor_agg_doc <- cor.behav(sel_grads_mcmc_flat$Aggression, 
  sel_grads_mcmc_flat$Docility)
cor_doc_act <- cor.behav(sel_grads_mcmc_flat$Docility, 
  sel_grads_mcmc_flat$Activity)
```

#### Aggression and Activity

```{r agg_act_mcmc, fig.height=2.03, fig.width=2.17}
p <- ggplot(data = sel_grads_mcmc_flat, aes(x = Activity, y = Aggression))
p <- p + geom_point()
p <- p + ylab("Aggression")
p <- p + xlab("Activity")
p <- p + theme_bw(base_size = 10)
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + geom_errorbarh(aes(xmin = Act_lower, xmax = Act_upper),
  height = 0.07, size = 0.2)
p <- p + geom_errorbar(aes(ymin = Agg_lower, ymax = Agg_upper),
  width = 0.07, size = 0.2)
p <- p + ylim(c(-1, 1.2))
p <- p + annotate(geom = "text", size = 3, x = 0.25, y = 1.2,
  label = paste("r = ", cor_agg_act, sep = ''))
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

#### Aggression and Docility

```{r agg_doc_mcmc, fig.height=2.03, fig.width=2.17}
p <- ggplot(data = sel_grads_mcmc_flat, aes(y = Aggression, x = Docility))
p <- p + geom_point()
p <- p + ylab("Aggression")
p <- p + xlab("Docility")
p <- p + theme_bw(base_size = 10)
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + geom_errorbarh(aes(xmin = Doc_lower, xmax = Doc_upper),
  height = 0.07, size = 0.2)
p <- p + geom_errorbar(aes(ymin = Agg_lower, ymax = Agg_upper),
  width = 0.03, size = 0.2)
p <- p + ylim(c(-1, 1.2))
p <- p + annotate(geom = "text", size = 3, x = -0.025, y = 1.2,
  label = paste("r = ", cor_agg_doc, sep = ''))
p <- p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
p + scale_x_continuous(limits = c(-0.6, 0.55),
  breaks = c(-0.5, -0.25, 0, 0.25, 0.5))
```

#### Activity and Docility

```{r act_doc_mcmc, fig.height=2.03, fig.width=2.17}
p <- ggplot(data = sel_grads_mcmc_flat, aes(x = Activity, y = Docility))
p <- p + geom_point()
p <- p + xlab("Activity")
p <- p + ylab("Docility")
p <- p + theme_bw(base_size = 10)
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + geom_errorbar(aes(ymin = Doc_lower, ymax = Doc_upper),
  width = 0.07, size = 0.2)
p <- p + geom_errorbarh(aes(xmin = Act_lower, xmax = Act_upper),
  height = 0.03, size = 0.2)
p <- p + ylim(c(-0.6,0.55))
p <- p + xlim(c(-1.1, 1.35))
p <- p + annotate(geom = "text", size = 3, x = 0, y = 0.55,
  label = paste("r = ", cor_doc_act, sep = ''))
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

### Summary Stats

```{r summary_stats, results='asis'}
library(dplyr)
sign_change <- function(x){
  # sign changes calculated as the number of changes in direction between 
  # successive years relative to n−1
  s <- sign(x)
  sum(s[1:(length(s)-1)] != s[-1])/(length(s)-1)
}
se <- function(lower, upper){
  (upper - lower) / 3.92
}

sum_stats_mcmc <- sel_grads_mcmc %>%
filter(standardization == "SD") %>%
group_by(variable, add = FALSE) %>%
summarise(
  mean_abs_b = mean(abs(post_mode)),
  abs_mean_b = abs(mean(post_mode)),
  sd_b = sd(post_mode),
  mean_se_b = mean(se(lower, upper)),
  freq_sign = sign_change(post_mode),
  mean_cv = mean(se(lower, upper) / abs(post_mode))
  )
sum_stats_mcmc[ ,2:6] <- round(sum_stats_mcmc[ ,2:6], 2)
pandoc.table(sum_stats_mcmc)
```

## Ignoring random effect uncertainty
Calculate selection gradients from BLUPs, estimate SE using jackknifing.

### Calculate selection gradients

```{r seCoeff}
# Calculate standardized selection gradients
seCoeffLmer <- function(x){
  model <- lm(rel_ars ~ aggression + activity + docility, data = x)
  model_sy <- lm(rel_ars ~ aggression_sy + activity_sy + docility_sy, data = x)
  mod_coefs <- c(coef(model)[-1], coef(model_sy)[-1])
  sim_coefs <- data.frame(coef(sim(model))[ ,-1], coef(sim(model_sy))[ ,-1]) ## Simulated coefficients for calculating uncertainty.
  names(sim_coefs) <- names(mod_coefs)
  sim_CI <- apply(sim_coefs, 2, quantile, prob = c(0.025, 0.975)) #0.95 conf. int.
  
docil_mean_coef <- mod_coefs["docility"] * mean(x$docility, na.rm = TRUE)
  out <- data.frame(
    standardization = c("None","None","None","SD","SD","SD","Mean"),
    Year = as.numeric(rep(as.character(x$Year[1]), 7)),
    variable = c("Aggression", "Activity", "Docility", "Aggression", 
      "Activity", "Docility", "Docility"),
    coefficients = c(mod_coefs, docil_mean_coef),
    lower = c(sim_CI[1, ], 0),
    upper = c(sim_CI[2, ],0)
    )
    return(out)
}

sel_grads_blup <- fit_raneff_data %>%
  filter(type == "blup") %>%
  group_by(Year, add = FALSE) %>%
  do(seCoeffLmer(.))
sel_grads_blup$variable <- as.character(sel_grads_blup$variable)
sel_grads_blup$Year <- as.character(sel_grads_blup$Year)
sel_grads_blup <- tbl_df(sel_grads_blup)
save(sel_grads_blup, file = "data/analyses_data/sel_grads_blup.RData")
```

```{r format_sel_grads_blup, results='asis'}
load("data/analyses_data/sel_grads_blup.RData")
# Format for table
sgt <- sel_grads_blup
sgt$sig_star <- ""
sgt$sig_star[sgt$coefficients > 0 & sgt$lower > 0] <- "*"
sgt$sig_star[sgt$coefficients < 0 & sgt$upper < 0] <- "*"
sgt$coefficients <- format(round(sgt$coefficients, digits = 2),
  digits = 1, nsmall = 2)
sgt$lower <- format(round(sgt$lower, digits = 2),
  digits = 1, nsmall = 2)
sgt$upper <- format(round(sgt$upper, digits = 2),
  digits = 1, nsmall = 2)
sgt$prb <- NA
sgt$coef <- paste(sgt$coefficients,
  " (", sgt$lower, " to ", sgt$upper,")", sgt$sig_star, sep = '')

sgt_agg <- filter(sgt, standardization == "None" & variable == "Aggression")
sgt_act <- filter(sgt, standardization == "None" & variable == "Activity")
sgt_doc <- filter(sgt, standardization == "None" & variable == "Docility")

sgt_agg_sd <- filter(sgt, standardization == "SD" &  variable == "Aggression")
sgt_act_sd <- filter(sgt, standardization == "SD" &  variable == "Activity")
sgt_doc_sd <- filter(sgt, standardization == "SD" &  variable == "Docility")

sgt_doc_ms <- filter(sgt, standardization == "Mean" &  variable == "Docility")

N <- fit_raneff_data %>%
  filter(type == "blup") %>%
  group_by(Year, add = FALSE) %>%
  summarise(n = n(), t_kprod = sum(kprod), t_ars = sum(ars_all), mean_docil = mean(docility, na.rm = TRUE))

pandoc.table(
  data.frame(
    Year = N$Year,
    Aggression = sgt_agg$coef,
    Activity = sgt_act$coef,
    Docility = sgt_doc$coef
  ),
  caption ="Traditional selection gradients (ignoring behavioural uncertainty). Not standardized."
)

pandoc.table(
  data.frame(
    Year = N$Year,
    Aggression = sgt_agg_sd$coef,
    Activity = sgt_act_sd$coef,
    Docility = sgt_doc_sd$coef
  ),
  caption ="Traditional selection gradients (ignoring behavioural uncertainty). SD-standardized."
)

pandoc.table(
  data.frame(
    Year = N$Year,
    Docility = sgt_doc_ms$coefficients,
    mean = N$mean_docil
  ),
  caption ="Traditional selection gradients (ignoring behavioural uncertainty). Mean-standardized."
)

```

### Plot
**Female Linear Selection Gradients ARS**  
Linear selection gradients ± 95% credible intervals for female behavioral traits on annual reproductive success.

```{r sel_grads_blup_plot, fig.width=6, fig.height=4}
load("data/analyses_data/sel_grads_blup.RData")
sel_grads_blup$post_mode <- sel_grads_blup$coefficients
sel_grads_blup$upper_sig_star <- ""
sel_grads_blup$lower_sig_star <- ""
sel_grads_blup$upper_sig_star[sel_grads_blup$coefficients > 0 & 
  sel_grads_blup$lower > 0] <- "*"
sel_grads_blup$lower_sig_star[sel_grads_blup$coefficients < 0 &
  sel_grads_blup$upper < 0] <- "*"
sel_grads_blup$upper_sig_01_star <- ""
sel_grads_blup$lower_sig_01_star <- ""
sel_grads_blup$upper_sig_01_star[sel_grads_blup$coefficients > 0
  & sel_grads_blup$lower_1 > 0] <- "."
sel_grads_blup$lower_sig_01_star[sel_grads_blup$coefficients < 0
  & sel_grads_blup$upper_1 < 0] <- "."
sel_grads_blup$upper_sig_01_star[sel_grads_blup$coefficients > 0
  & sel_grads_blup$lower > 0] <- ""
sel_grads_blup$lower_sig_01_star[sel_grads_blup$coefficients < 0
  & sel_grads_blup$upper < 0] <- ""

pdf(file = "figure/sel_grads_blup_plot.pdf", width = 4.33, height = 3)
p <- p_sel_grad_MCMC %+% filter(sel_grads_blup, standardization == "SD")
p <- p + ylab("Coefficient ± 0.95 Confidence Interval")
p <- p + geom_text(aes(x = Year, y = upper, group = variable,
  label = upper_sig_01_star), vjust = -0.3,
  position = position_dodge(width = 0.5), size = 7)
p <- p + geom_text(aes(x = Year, y = lower, group = variable,
  label = lower_sig_01_star), vjust =  0.5,
  position = position_dodge(width = 0.5), size = 7)
p <- p + geom_text(aes(x = Year, y = upper, group = variable,
  label = upper_sig_star), vjust = -0.3,
  position = position_dodge(width = 0.5), size = 5)
p <- p + geom_text(aes(x = Year, y = lower, group = variable,
  label = lower_sig_star), vjust =  1.3,
  position = position_dodge(width = 0.5), size = 5)
p <- p + ylim(c(-2, 2))
p <- p + scale_shape_manual(name = "A", values = c(24, 21, 22))
p <- p + scale_fill_manual(name = "A", values = c("white", "black", "white"))
p <- p + scale_color_manual(name = "A", values = c("black", "black", "black"))
p
dev.off()
p
```

### Correlations
```{r sg_cors_blup, fig.width=5, fig.height=5}
load("data/analyses_data/sel_grads_blup.RData")
sel_grads_blup_flat <- data.frame(
  Aggression = filter(sel_grads_blup, standardization == "SD" &
   variable == "Aggression")$coefficients,
  Agg_upper  = filter(sel_grads_blup, standardization == "SD" &
   variable == "Aggression")$upper,
  Agg_lower  = filter(sel_grads_blup, standardization == "SD" &
   variable == "Aggression")$lower,
  Activity   = filter(sel_grads_blup, standardization == "SD" &
   variable == "Activity")$coefficients,
  Act_upper  = filter(sel_grads_blup, standardization == "SD" &
   variable == "Activity")$upper,
  Act_lower  = filter(sel_grads_blup, standardization == "SD" &
   variable == "Activity")$lower,
  Docility   = filter(sel_grads_blup, standardization == "SD" &
   variable == "Docility")$coefficients,
  Doc_upper  = filter(sel_grads_blup, standardization == "SD" &
   variable == "Docility")$upper,
  Doc_lower  = filter(sel_grads_blup, standardization == "SD" &
   variable == "Docility")$lower
)

cor.behav <- function(x, y){
  ct <- cor.test(x, y)
  out <- data.frame(est = ct$estimate, lower = ct$conf.int[1],
    upper = ct$conf.int[2], stringsAsFactors = FALSE)
  out <- round(out, digits = 2)
  out$print <- paste(out$est, " (", out$lower, ", ", out$upper, ")", sep = "")
}

cor_blup_agg_act <- cor.behav(sel_grads_blup_flat$Aggression,
  sel_grads_blup_flat$Activity)
cor_blup_agg_doc <- cor.behav(sel_grads_blup_flat$Aggression,
  sel_grads_blup_flat$Docility)
cor_blup_doc_act <- cor.behav(sel_grads_blup_flat$Docility,
  sel_grads_blup_flat$Activity)
```

#### Aggression and Activity
```{r agg_act_blup, fig.height=2.03, fig.width=2.17}
p <- ggplot(data = sel_grads_blup_flat, aes(x = Activity, y = Aggression))
p <- p + geom_point()
p <- p + ylab("Aggression")
p <- p + xlab("Activity")
p <- p + theme_bw(base_size = 10)
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + geom_errorbarh(aes(xmin = Act_lower, xmax = Act_upper),
  height = 0.07, size = 0.2)
p <- p + geom_errorbar(aes(ymin = Agg_lower, ymax = Agg_upper),
  width = 0.07, size = 0.2)
p <- p + xlim(c(-1.8,2))
p <- p + ylim(c(-1.4, 1.6))
p <- p + annotate(geom = "text", size = 2.5, x = 0.25, y = 1.6,
  label = paste("r = ", cor_blup_agg_act, sep = ''))
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

#### Aggression and Docility
```{r agg_doc_blup, fig.height=2.03, fig.width=2.17}
p <- ggplot(data = sel_grads_blup_flat, aes(y = Aggression, x = Docility))
p <- p + geom_point()
p <- p + ylab("Aggression")
p <- p + xlab("Docility")
p <- p + theme_bw(base_size = 10)
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + geom_errorbarh(aes(xmin = Doc_lower, xmax = Doc_upper),
  height = 0.07, size = 0.2)
p <- p + geom_errorbar(aes(ymin = Agg_lower, ymax = Agg_upper),
  width = 0.03, size = 0.2)
p <- p + xlim(c(-1.1,1))
p <- p + ylim(c(-1.4, 1.6))
p <- p + annotate(geom = "text", size = 2.5, x = 0.2, y = 1.6,
  label = paste("r = ", cor_blup_agg_doc, sep = ''))
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

#### Activity and Docility
```{r act_doc_blup, fig.height=2.03, fig.width=2.17}
p <- ggplot(data = sel_grads_blup_flat, aes(x = Activity, y = Docility))
p <- p + geom_point()
p <- p + xlab("Activity")
p <- p + ylab("Docility")
p <- p + theme_bw(base_size = 10)
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + geom_errorbar(aes(ymin = Doc_lower, ymax = Doc_upper),
  width = 0.07, size = 0.2)
p <- p + geom_errorbarh(aes(xmin = Act_lower, xmax = Act_upper),
  height = 0.03, size = 0.2)
p <- p + scale_y_continuous(limits = c(-1.1, 1), breaks = c(-1, 0, 1))
p <- p + xlim(c(-1.8, 2))
p <- p + annotate(geom = "text", size = 2.5, x = 0, y = 1,
  label = paste("r = ", cor_blup_doc_act, sep = ''))
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

### Summary Statistics
```{r summary_blup, results='asis'}
sum_stats_blup <- sel_grads_blup %>%
filter(standardization == "SD") %>%
group_by(variable, add = FALSE) %>%
summarise(
  mean_abs_b = mean(abs(coefficients)),
  abs_mean_b = abs(mean(coefficients)),
  sd_b = sd(coefficients),
  mean_se_b = mean(se(lower, upper)),
  freq_sign = sign_change(coefficients),
  mean_cv = mean(se(lower, upper) / abs(coefficients))
  )
sum_stats_blup[ ,2:6] <- round(sum_stats_blup[ ,2:6], 2)
pandoc.table(sum_stats_blup)
```

## Compare Analytical Frameworks

### Table
```{r compare, results='asis'}
load("data/analyses_data/sel_grads_blup.RData")
load("data/analyses_data/sel_grads_mcmc.RData")

sg_blups <- sel_grads_blup %>% filter(standardization == "SD")
sg_mcmc <- sel_grads_mcmc %>% filter(standardization == "SD")

compare_grads <- left_join(select(sg_blups, Year, variable,
  blup_coef = coefficients, blup_upper = upper, blup_lower = lower),
  select(sg_mcmc, Year, variable, mcmc_pm = post_mode,
    mcmc_upper = upper, mcmc_lower = lower), by = c("variable", "Year"))

ct_print <- function(x,y){
  ct <- cor.test(x,y)
  est <- format(ct$estimate, digits = 2)
  ci <- format(ct$conf.int, digits = 2)
  ct <- format(ct, digits = 2)
  paste(est, " (", ci[1], ", ", ci[2] ,")", sep = '')  
}

c_table <- compare_grads %>%
  group_by(variable) %>%
  summarise(cor = cor(blup_coef, mcmc_pm),
    abs_diff = mean((abs(blup_coef - mcmc_pm))),
    mean_mcmc = mean(abs(mcmc_pm)), mean_blup = mean(abs(blup_coef)),
    prop_diff = mean_blup / mean_mcmc, cor_test = ct_print(blup_coef, mcmc_pm),
    lmerGreater = sum(abs(blup_coef) > abs(mcmc_pm))
  )
pandoc.table(c_table)
```

### Aggression plot
```{r compare_agg, fig.height=2.3, fig.width=2.17}
p <- ggplot(filter(compare_grads, standardization == "SD" & variable == "Aggression"),
  aes(x = blup_coef, y = mcmc_pm))
p <- p + geom_point()
p <- p + geom_errorbarh(aes(xmin = blup_lower, xmax = blup_upper),
  height = 0.04, size = 0.2)
p <- p + geom_errorbar(aes(ymin = mcmc_lower, ymax = mcmc_upper),
  width = 0.07, size = 0.2)
p <- p + theme_bw(base_size = 10)
p <- p + theme(plot.title = element_text(size = 10),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), strip.background = element_blank(),
  strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + annotate(geom = "text", size = 2.5, x = 0, y = 1.5,
  label = paste("r = ", filter(c_table, variable == "Aggression") %>%
  select(cor_test), sep = ''))
p <- p + ylab("Posterior Modes")
p <- p + xlab("Selection Gradients")
p <- p + xlim(c(-1.4, 1.5))
p <- p + ylim(c(-1.4, 1.5))
p <- p + ggtitle("Aggression")
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

### Activity Plot
```{r compare_act, fig.height=2.3, fig.width=2.17}
p <- ggplot(filter(compare_grads, standardization == "SD" & variable == "Activity"),
  aes(x = blup_coef, y = mcmc_pm))
p <- p + geom_point()
p <- p + geom_errorbarh(aes(xmin = blup_lower, xmax = blup_upper),
  height = 0.04, size = 0.2)
p <- p + geom_errorbar(aes(ymin = mcmc_lower, ymax = mcmc_upper),
  width = 0.07, size = 0.2)
p <- p + theme_bw(base_size = 10)
p <- p + theme(plot.title = element_text(size = 10),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), strip.background = element_blank(),
  strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + annotate(geom = "text", size = 2.5, x = 0, y = 2,
  label = paste("r = ", filter(c_table, variable == "Activity") %>%
  select(cor_test), sep = ''))
p <- p + ylab("Posterior Modes")
p <- p + xlab("Selection Gradients")
p <- p + xlim(c(-1.8,2))
p <- p + ylim(c(-1.8,2))
p <- p + ggtitle("Activity")
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

### Docility Plot
```{r compare_doc, fig.height=2.3, fig.width=2.17}
p <- ggplot(filter(compare_grads, standardization == "SD" & variable == "Docility"),
  aes(x = blup_coef, y = mcmc_pm))
p <- p + geom_point()
p <- p + geom_errorbarh(aes(xmin = blup_lower, xmax = blup_upper),
  height = 0.04, size = 0.2)
p <- p + geom_errorbar(aes(ymin = mcmc_lower, ymax = mcmc_upper),
  width = 0.07, size = 0.2)
p <- p + theme_bw(base_size = 10)
p <- p + theme(plot.title = element_text(size = 10),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), strip.background = element_blank(),
  strip.text = element_blank(),
  panel.border = element_rect(linetype = "solid", colour = "black"))
p <- p + ylab("Posterior Modes")
p <- p + xlab("Selection Gradients")
p <- p + xlim(c(-1.1,0.9)) 
p <- p + scale_y_continuous(limits = c(-1.1, 1), breaks = c(-1, 0, 1))
p <- p + annotate(geom = "text", size = 2.5, x = 0, y = 1,
  label = paste("r = ", filter(c_table, variable == "Docility") %>%
  select(cor_test), sep = ''))
p <- p + ggtitle("Docility")
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```