<!--pandoc
t: html
default-image-extension: png
template: templates/html.template
toc-depth: 4
toc:

t: latex
s:
S:
latex-engine: xelatex
template: templates/latex.template
default-image-extension: pdf
toc-depth: 4
toc:
-->

# Competition and Selection
```{r echo=FALSE, cache=FALSE, results="hide"}
opts_chunk$set(cache=TRUE, fig.cap='', dev=c('png', 'pdf'), fig.width=6,
  fig.height=4)
opts_knit$set('upload.fun' = function(x) sub("\\.[[:alnum:]]*$", "", x) )
opts_chunk$set(cache.path="cache/05/")
```

## Accounting for behavioral measurement uncertainty

```{r comp_data, cache=FALSE}
library(ggplot2)
library(grid)
library(dplyr)
library(pander)
set.alignment('right', row.names = 'left')
load("data/analyses_data/sel_grads_mcmc.RData")
fitness <- read.table(file = "data/fitness+competition.csv", sep = ',',
  header = TRUE, stringsAsFactors = FALSE)
load("data/analyses_data/fit_raneff_data.RData")
```

We will examine the effect of competition on selection in two general steps.

  1. Is there an interaction between competition and behavior on fitness?
  2. Are there nonlinear effects of behavior on fitness?


### Correlations between selection gradients and competition
First a plot of the relationship between selection gradients and competition. The two study areas were pooled to calculate selection gradients for each year. Therefore we need to calculate competition for the combined study areas. Competition is the number of offspring produced during the year divided by the number of offspring that survived to spring (i.e. recruited into the population).

```{r mean_comp}
competition_year <- fitness %>%
  filter(grid_year != "SU2008") %>%
  select(Year, competition) %>%
  unique() %>%
  group_by(Year, add = FALSE) %>%
  summarise(mean_competition = mean(competition))
  
n_year <- filter(fit_raneff_data, type == "blup") %>%
  group_by(Year, add = FALSE) %>% summarise(n = n())
competition_year <- left_join(competition_year, n_year, by = "Year")
competition_year$Year <- as.character(competition_year$Year)

load("data/analyses_data/sel_grads_mcmc.RData")
sel_grads_mcmc_comp <- left_join(sel_grads_mcmc, competition_year,
  by = "Year")
save(sel_grads_mcmc_comp, competition_year,
  file = "data/analyses_data/sel_grads_mcmc_comp.RData")
```

```{r calc_correlations}
load("data/analyses_data/sel_grads_mcmc_comp.RData")

cor_sgrad_comp <- function(x){
  v <- x$variable[1]
  ct <- cor.test(x$post_mode, x$mean_competition)
  data.frame(variable = v, est = ct$estimate, lower = ct$conf.int[1],
    upper = ct$conf.int[2], stringsAsFactors = FALSE)
}

mcmc_cor <- sel_grads_mcmc_comp %>%
  group_by(variable, add = FALSE) %>%
  do(cor_sgrad_comp(.))
mcmc_cor[ ,2:4] <- round(mcmc_cor[ ,2:4], digits = 2)
mcmc_cor$print <- paste(mcmc_cor$est,
  " (", mcmc_cor$lower, ", ", mcmc_cor$upper, ")", sep = "")
```
#### Aggression and Competition

```{r agg_comp_mcmc, fig.height=2.3, fig.width=2.17}
p <- ggplot(data = filter(sel_grads_mcmc_comp, variable == "Aggression"),
  aes(x = mean_competition, y = post_mode))
p <- p + geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 0.2)
p <- p + geom_point()
p <- p + theme_bw(base_size = 10)
p <- p + scale_x_continuous(breaks = c(3,4,5,6,7,8,9))
p <- p + ylab("Selection Gradient")
p <- p + ggtitle("Aggression")
p <- p + xlab("Juvenile Competition")
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_text(size = 10),
  panel.border = element_rect(linetype = "solid", colour = "black"),
  plot.title = element_text(size = 10))
p <- p + ylim(c(-1, 1))
p <- p + geom_text(data = filter(mcmc_cor, variable == "Aggression"),
  aes(x = 6.5, y = 1, label = paste("Correlation = ", print, sep = '')),
  size = 2.5)
p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

#### Activity and Competition
```{r act_comp_mcmc, fig.height=2.3, fig.width=2.17}
p <- ggplot(data = filter(sel_grads_mcmc_comp, variable == "Activity"),
  aes(x = mean_competition, y = post_mode))
p <- p + geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 0.2)
p <- p + geom_point()
p <- p + theme_bw(base_size = 10)
p <- p + scale_x_continuous(breaks = c(3,4,5,6,7,8,9))
p <- p + ylab("Selection Gradient")
p <- p + ggtitle("Activity")
p <- p + xlab("Juvenile Competition")
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_text(size = 10),
  panel.border = element_rect(linetype = "solid", colour = "black"),
  plot.title = element_text(size = 10))
p <- p + ylim(c(-1, 1.5))
p <- p + geom_text(data = filter(mcmc_cor, variable == "Activity"),
  aes(x = 6.5, y = 1.5, label = paste("Correlation = ", print, sep = '')),
  size = 3.5)
p <- p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

#### Docility and Competition
```{r doc_comp_mcmc, fig.height=2.3, fig.width=2.17}
p <- ggplot(data = filter(sel_grads_mcmc_comp, variable == "Docility"),
  aes(x = mean_competition, y = post_mode))
p <- p + geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 0.2)
p <- p + geom_point()
p <- p + theme_bw(base_size = 10)
p <- p + scale_x_continuous(breaks = c(3,4,5,6,7,8,9))
p <- p + ylab("Selection Gradient")
p <- p + ggtitle("Docility")
p <- p + xlab("Juvenile Competition")
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_text(size = 10),
  panel.border = element_rect(linetype = "solid", colour = "black"),
  plot.title = element_text(size = 10))
p <- p + ylim(c(-0.60, 0.60))
p <- p + geom_text(data = filter(mcmc_cor, variable == "Docility"),
  aes(x = 6.5, y = 0.60, label = paste("Correlation = ", print, sep = '')),
  size = 3.5)
p <- p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
```

### Effect of competition on linear selection (glmms)
```{r Competition_glmms_mcmc}
load("data/analyses_data/fit_raneff_data.RData")
library(dplyr)
fit_raneff_data <- tbl_df(fit_raneff_data)
library(lme4)

# Model with interactions between competition and the behavioral traits. 
# grid_year and ID are random effects.
arsLinearCompetition <- function(dat){
  ars_linear_comp <- glmer(
  	ars_all ~ 
  	competition_s + 
  	aggression_s + 
  	competition_s:aggression_s + 
  	activity_s + 
  	competition_s:activity_s + 
  	docility_s +
  	competition_s:docility_s +
    (1|Grid) + (1|ID),
  	data = dat, family = poisson, control=glmerControl(optimizer="bobyqa")
  	)
  random_effect_variances <- VarCorr(ars_linear_comp)
  data.frame(t(summary(ars_linear_comp)$coefficients[ ,"Estimate"]),
  ID = random_effect_variances$ID[1], Grid = random_effect_variances$Grid[1])
}

library(foreach)
library(doMC)
ncores = 12
registerDoMC(cores = ncores)

batches <- data.frame(start = seq(1, 1000, round(1000/ncores))[1:ncores])
batches$stop <- c(batches$start[2:length(batches$start)] - 1, 1000)

start_time <- Sys.time()
ars_linear_comp_posterior <- foreach(i = 1:ncores, .combine = rbind) %dopar% {
  results <- fit_raneff_data %>%
    filter(type == "raneff", itt %in% batches$start[i]:batches$stop[i]) %>%
    group_by(itt, add = FALSE) %>%
    do(arsLinearCompetition(.))
}
run_time <- Sys.time() - start_time
print(run_time)

save(ars_linear_comp_posterior,
  file = "data/analyses_data/ars_linear_comp_posterior.RData")
```

```{r format_ac}
load("data/analyses_data/ars_linear_comp_posterior.RData")
library(MCMCglmm)
library(lme4)
library(data.table)

getPosteriorParams <- function(x){
  require(MCMCglmm)
  dat_mcmc <- mcmc(x)
  pm <- posterior.mode(dat_mcmc)
  hpd <- HPDinterval(dat_mcmc, prob = 0.9)
  pm_table <-  format(round(pm , digits = 2), digits = 1, nsmall = 2,
    scientific = FALSE)
  hpd_table <- format(round(hpd, digits = 2), digits = 1, nsmall = 2,
    scientific = FALSE)
  pm_hpd_table <- data.frame(cbind(pm_table, hpd_table))
  pm_hpd_table$pm_hpd <- paste(
    pm_table, " (", hpd_table[ ,1], ", ", hpd_table[ ,2], ")", sep = ''
    )
  pm_hpd_table$sig[sign(hpd[ ,1]) == sign(hpd[ ,2])] <- "*"
  pm_hpd_table$sig[sign(hpd[ ,1]) != sign(hpd[ ,2])] <- " "
  pm_hpd_table$space[sign(hpd[ ,1]) == sign(hpd[ ,2])] <- "*"
  pm_hpd_table$space[sign(hpd[ ,1]) != sign(hpd[ ,2])] <- "&nbsp;"
  pm_hpd_table$pm_hpd <- paste(pm_hpd_table$pm_hpd, pm_hpd_table$sig, sep = "")
  return(pm_hpd_table)
}

linear_hpd_ars <- getPosteriorParams(ars_linear_comp_posterior %>%
  ungroup() %>%
  select(Intercept = X.Intercept., Competition = competition_s,
    Aggression = aggression_s, Activity = activity_s, docility = docility_s,
    "Competition x Aggression" = competition_s.aggression_s,
    "Competition x Activity" = competition_s.activity_s,
    "Competition x Docility" = competition_s.docility_s)
    )
```

#### Interaction between competition and linear selection results

The effect of competition on linear selection on female behavioral traits for annual reproductive success. Posterior modes are given with highest posterior density intervals in parentheses.

```{r linear_hpd_ars_table, results='asis'}
pandoc.table(linear_hpd_ars %>% select(pm_hpd), justify="right")
```

### Competition and nonlinear selection (glmms)

```{r nonlinear_models}
load("data/analyses_data/fit_raneff_data.RData")
library(lme4)

arsNonlinearResults <- function(dat){
  ars_model  <- glmer(ars_all ~ aggression_s*competition_s +
    activity_s*competition_s + docility_s*competition_s +
    aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s +
    I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
    (1 | grid_year) + (1|ID), data = dat, family = poisson,
    control=glmerControl(optimizer="bobyqa"))
  kpd_model  <- glmer(kprod   ~ aggression_s*competition_s +
    activity_s*competition_s + docility_s*competition_s +
    aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s +
    I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
    (1 | grid_year) + (1|ID), data = dat, family = poisson,
    control=glmerControl(optimizer="bobyqa"))
  ows_model  <- glmer(prop    ~ aggression_s*competition_s +
    activity_s*competition_s + docility_s*competition_s +
    aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s +
    I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
    (1 | grid_year) + (1|ID), data = dat, weights = kprod, family = binomial,
    control=glmerControl(optimizer="bobyqa"))

  ars_vc <- VarCorr(ars_model)
  ars_t <- data.table(fitness = "ars",
    t(summary(ars_model)$coefficients[ ,"Estimate"]), ID = ars_vc$ID[1],
    grid_year = ars_vc$grid_year[1])
  kpd_vc <- VarCorr(kpd_model)
  kpd_t <- data.table(fitness = "kpd",
    t(summary(kpd_model)$coefficients[ ,"Estimate"]), ID = kpd_vc$ID[1],
    grid_year = kpd_vc$grid_year[1])
  ows_vc <- VarCorr(ows_model)
  ows_t <- data.table(fitness = "ows",
    t(summary(ows_model)$coefficients[ ,"Estimate"]), ID = ows_vc$ID[1],
    grid_year = ows_vc$grid_year[1])
  rbind(rbind(ars_t, kpd_t), ows_t)
}


library(foreach)
library(doMC)
ncores = 12
registerDoMC(cores = ncores)

batches <- data.frame(start = seq(1, 1000, round(1000/ncores))[1:ncores])
batches$stop <- c(batches$start[2:length(batches$start)] - 1, 1000)

start_time <- Sys.time()
nonlinear_mcmc <- foreach(i = 1:ncores, .combine = rbind) %dopar% {
  results <- fit_raneff_data %>%
    filter(type == "raneff", itt %in% batches$start[i]:batches$stop[i]) %>%
    group_by(itt, add = FALSE) %>%
    do(arsNonlinearResults(.))
}
run_time <- Sys.time() - start_time
print(run_time)

save(nonlinear_mcmc, file = "data/analyses_data/nonlinear_mcmc_models.RData")
```

```{r format_for_tables}
load("data/analyses_data/nonlinear_mcmc_models.RData")

pm_hpd_ars <- getPosteriorParams(
  nonlinear_mcmc[nonlinear_mcmc$fitness =="ars", 3:18])
pm_hpd_ows <- getPosteriorParams(
  nonlinear_mcmc[nonlinear_mcmc$fitness =="ows", 3:18])
pm_hpd_kpd <- getPosteriorParams(
  nonlinear_mcmc[nonlinear_mcmc$fitness =="kpd", 3:18])

nonlinear_results_mcmc <- data.frame(ARS = pm_hpd_ars$pm_hpd,
  OWS = pm_hpd_ows$pm_hpd, Fecundity = pm_hpd_kpd$pm_hpd)
  
row.names(nonlinear_results_mcmc) <- c("Intercept", "Aggression",
 "Competition", "Activity", "Docility", "Aggression^2", "Activity^2",
 "Docility^2", "Aggression x Competition", "Activity x Competition",
 "Docility x Competition", "Aggression x Activity",
 "Aggression^2 x Competition", "Activity^2 x Competition",
 "Docility^2 x Competition", "Agg. x Act. x Competition"
 )
```

### Nonlinear results
The effect of competition on linear and nonlinear selection on female behavioral traits for annual reproductive success. Posterior modes are given with highest posterior density intervals in parentheses.

```{r nonlinear_results_mcmc, results='asis'}
pandoc.table(nonlinear_results_mcmc[c(1,3,2,4:16), ], 
  split.tables = 160)
```

## Ignoring behavioural uncertainty
```{r load_blup_data}
load("data/analyses_data/sel_grads_blup.RData")
load("data/analyses_data/fit_raneff_data.RData")
```

### Correlations between selection gradients and competition
```{r mean_comp_blup}
competition_year <- fitness %>%
  filter(grid_year != "SU2008") %>%
  select(Year, competition) %>%
  unique() %>%
  group_by(Year, add = FALSE) %>%
  summarise(mean_competition = mean(competition))
  
n_year <- filter(fit_raneff_data, type == "blup") %>%
  group_by(Year, add = FALSE) %>%
  summarise(n = n())
competition_year <- left_join(competition_year, n_year, by = "Year")
competition_year$Year <- as.character(competition_year$Year)

load("data/analyses_data/sel_grads_blup.RData")
sel_grads_blup_competition <- left_join(sel_grads_blup, competition_year,
  by = "Year")
save(sel_grads_blup_competition, competition_year,
  file = "data/analyses_data/sel_grads_blup_competition.RData")
```

```{r comp_sg_plot_blup, fig.width=4.33, fig.height=4.5, fig.cap = ""}
load("data/analyses_data/sel_grads_blup_competition.RData")

cor_sgrad_comp <- function(x){
  v <- x$variable[1]
  ct <- cor.test(x$coefficients, x$mean_competition)
  data.frame(variable = v, est = ct$estimate, lower = ct$conf.int[1],
    upper = ct$conf.int[2], stringsAsFactors = FALSE)
}

sg.comp <- sel_grads_blup_competition %>%
  group_by(variable, add = FALSE) %>%
  do(cor_sgrad_comp(x=.))
sg.comp[ ,2:4] <- round(sg.comp[ ,2:4], digits = 2)
sg.comp$print <- paste(sg.comp$est, " (", sg.comp$lower, ", ",
  sg.comp$upper, ")", sep = "")
```

#### Aggression and Competition

```{r agg_comp_blup, fig.height=2.3, fig.width=2.17}
p <- ggplot(data = filter(sel_grads_blup_competition,
  variable == "Aggression"), aes(x = mean_competition, y = coefficients))
p <- p + geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 0.2)
p <- p + geom_point()
p <- p + theme_bw(base_size = 10)
p <- p + scale_x_continuous(breaks = c(3,4,5,6,7,8,9))
p <- p + ylab("Selection Gradient")
p <- p + ggtitle("Aggression")
p <- p + xlab("Juvenile Competition")
p <- p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), strip.background = element_blank(), strip.text = element_text(size = 10), panel.border = element_rect(linetype = "solid", colour = "black"), plot.title = element_text(size = 10))
p <- p + ylim(c(-1.4, 1.5))
p <- p + geom_text(data = filter(sg.comp, variable == "Aggression"),
  aes(x = 6, y = 1.5, label = paste("r = ", print, sep = '')), size = 2.5)
p <- p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
p
```

#### Activity and Competition

```{r act_comp_blup, fig.height=2.3, fig.width=2.17}
p <- ggplot(data = filter(sel_grads_blup_competition, variable == "Activity"), 
  aes(x = mean_competition, y = coefficients))
p <- p + geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 0.2)
p <- p + geom_point()
p <- p + theme_bw(base_size = 10)
p <- p + scale_x_continuous(breaks = c(3,4,5,6,7,8,9))
p <- p + ylab("Selection Gradient")
p <- p + ggtitle("Activity")
p <- p + xlab("Juvenile Competition")
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_text(size = 10),
  panel.border = element_rect(linetype = "solid", colour = "black"),
  plot.title = element_text(size = 10))
p <- p + ylim(c(-1.9, 2.1))
p <- p + geom_text(data = filter(sg.comp, variable == "Activity"),
  aes(x = 6, y = 2.1, label = paste("r = ", print, sep = '')), size = 2.5)
p <- p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
p
```

#### Docility and Competition

```{r doc_comp_blup, fig.height=2.3, fig.width=2.17}
p <- ggplot(data = filter(sel_grads_blup_competition, variable == "Docility"),
  aes(x = mean_competition, y = coefficients))
p <- p + geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 0.2)
p <- p + geom_point()
p <- p + theme_bw(base_size = 10)
p <- p + scale_x_continuous(breaks = c(3,4,5,6,7,8,9))
p <- p + ylab("Selection Gradient")
p <- p + ggtitle("Docility")
p <- p + xlab("Juvenile Competition")
p <- p + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), panel.background = element_blank(),
  strip.background = element_blank(), strip.text = element_text(size = 10),
  panel.border = element_rect(linetype = "solid", colour = "black"),
  plot.title = element_text(size = 10))
p <- p + scale_y_continuous(limits = c(-1.1, 1), breaks = c(-1, 0, 1))
p <- p + geom_text(data = filter(sg.comp, variable == "Docility"),
  aes(x = 6, y = 1, label = paste("r = ", print, sep = '')), size = 2.5)
p <- p + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))
p
```

### Effect of competition on linear selection
```{r Competition_glmms_blup, eval=TRUE}
load("data/analyses_data/fit_raneff_data.RData")
library(dplyr)
fit_raneff_data <- tbl_df(fit_raneff_data)
library(lme4)
fit_raneff_data$oID <- 1:nrow(fit_raneff_data)

ars_linear_model  <- glmer(ars_all ~ aggression_s*competition_s +
  activity_s*competition_s + docility_s*competition_s + (1 | grid_year) +
  (1|ID) + (1|oID), data = filter(fit_raneff_data, type == "blup"),
  family = poisson, control=glmerControl(optimizer="bobyqa"))
kpd_linear_model  <- glmer(kprod ~ aggression_s*competition_s +
  activity_s*competition_s + docility_s*competition_s + (1 | grid_year) +
  (1|ID) + (1|oID), data = filter(fit_raneff_data, type == "blup"),
  family = poisson, control=glmerControl(optimizer="bobyqa"))
ows_linear_model  <- glmer(prop ~ aggression_s*competition_s +
  activity_s*competition_s + docility_s*competition_s + (1 | grid_year) +
  (1|ID) + (1|oID), data = filter(fit_raneff_data, type == "blup"),
  weights = kprod, family = binomial, control=glmerControl(optimizer="bobyqa"))

save(ars_linear_model, kpd_linear_model, ows_linear_model,
  file = "data/analyses_data/ars_linear_blup_models.RData")
```

Models with observation level random effect.

```{r Competition_glmms_overdispersed_blup}
load("data/analyses_data/fit_raneff_data.RData")
library(dplyr)
fit_raneff_data <- tbl_df(fit_raneff_data)
library(lme4)

fit_raneff_data$oID <- 1:nrow(fit_raneff_data)

ars_linear_model_  <- glmer(ars_all ~ aggression_s*competition_s +
  activity_s*competition_s + docility_s*competition_s + (1 | oID) +
  (1 | grid_year) + (1|ID), data = filter(fit_raneff_data, type == "blup"),
  family = poisson, control=glmerControl(optimizer="bobyqa"))
kpd_linear_model_  <- glmer(kprod   ~ aggression_s*competition_s +
  activity_s*competition_s + docility_s*competition_s + (1 | oID) +
  (1 | grid_year) + (1|ID), data = filter(fit_raneff_data, type == "blup"), 
  family = poisson, control=glmerControl(optimizer="bobyqa"))
ows_linear_model_  <- glmer(prop    ~ aggression_s*competition_s +
  activity_s*competition_s + docility_s*competition_s + (1 | oID) +
  (1 | grid_year) + (1|ID), data = filter(fit_raneff_data, type == "blup"), 
  weights = kprod, family = binomial, control=glmerControl(optimizer="bobyqa"))

save(ars_linear_model, kpd_linear_model, ows_linear_model,
  file = "data/analyses_data/ars_linear_blup_models.RData")
```

```{r format_ac_blup}
load("data/analyses_data/ars_linear_blup_models.RData")
library(lme4)

getLmerParams <- function(x){
  coefs <- summary(x)$coefficients
  coef.table <- data.frame(format(coefs[ ,1:3], digits = 1, nsmall = 2, 
    scientific = FALSE))
  coef.table$pval[coefs[ ,4] > 0.001] <- format(coefs[coefs[ ,4] > 0.001, 4], 
    digits = 1, nsmall = 2)
  coef.table$pval[coefs[ ,4] < 0.001] <- "< 0.001"
  coef.table$coefs <- paste(coef.table$Estimate, " ±", coef.table$Std..Error, 
    sep = '')
  return(coef.table)
}

ars_linear_blup_results <- getLmerParams(ars_linear_model)
row.names(ars_linear_blup_results) <- c("Intercept", "Aggression",
  "Competition", "Activity", "Docility", "Aggression x Competition",
  "Activity x Competition", "Docility x Competition")
names(ars_linear_blup_results) <- c("Estimate", "SE", "Z", "P", "Est ± se")
```

#### Interaction between competition and linear selection results

```{r ars_linear_blup_results, results = 'asis'}
pandoc.table(ars_linear_blup_results[c(1,3,2,4:8), c(5,4,3)],
  justify = "right", split.tables = 160)
```

### Competition and nonlinear selection

```{r nonlinear_models_blup}
load("data/analyses_data/fit_raneff_data.RData")
library(lme4)
fit_blups_data <- filter(fit_raneff_data, type == "blup")
fit_blups_data$oID <- 1:nrow(fit_blups_data)

ars_nl_model <- glmer(ars_all ~ aggression_s*competition_s + 
  activity_s*competition_s + docility_s*competition_s + 
  aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s + 
  I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
  (1 | grid_year) + (1|ID) + (1|oID),
  data = fit_blups_data, family = poisson,
  control=glmerControl(optimizer="bobyqa"))

ars_nl_model <- glmer(ars_all ~ aggression_s*competition_s + 
  activity_s*competition_s + docility_s*competition_s + 
  aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s + 
  I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
  (1 | grid_year) + (1|ID),
  data = fit_blups_data, family = poisson,
  control=glmerControl(optimizer="bobyqa"))
  
kpd_nl_model <- glmer(kprod ~ aggression_s*competition_s + 
  activity_s*competition_s + docility_s*competition_s + 
  aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s + 
  I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
  (1 | grid_year) + (1|ID) + (1|oID),
  data = fit_blups_data, family = poisson,
  control=glmerControl(optimizer="bobyqa"))
  
ows_nl_model <- glmer(prop ~ aggression_s*competition_s + 
  activity_s*competition_s + docility_s*competition_s + 
  aggression_s*activity_s*competition_s + I(aggression_s^2)*competition_s + 
  I(activity_s^2)*competition_s + I(docility_s^2)*competition_s +
  (1 | grid_year) + (1|ID) + (1|oID),
  data = fit_blups_data, weights = kprod,
  family = binomial,
  control=glmerControl(optimizer="bobyqa"))

save(ars_nl_model,kpd_nl_model, ows_nl_model,
  file = "data/analyses_data/nl.blup_models.RData")

fit_raneff_data %>%
  ungroup() %>%
  summarise(
    mean_ars = mean(ars_all, na.rm = TRUE),
    var_ars = var(ars_all, na.rm = TRUE),
    mean_kpd = mean(kprod, na.rm = TRUE),
    var_kpd = var(kprod, na.rm = TRUE)
    )
```

#### Format results of nonlinear selection for table
```{r format_for_tables_blup}
load("data/analyses_data/nl.blup_models.RData")

coef_p_ars <- getLmerParams(ars_nl_model)
coef_p_ows <- getLmerParams(ows_nl_model)
coef_p_kpd <- getLmerParams(kpd_nl_model)

term_names <- c("Intercept", "Aggression",
 "Competition", "Activity", "Docility", "Aggression^2", "Activity^2",
 "Docility^2", "Aggression x Competition", "Activity x Competition",
 "Docility x Competition", "Aggression x Activity",
 "Aggression^2 x Competition", "Activity^2 x Competition",
 "Docility^2 x Competition", "Agg. x Act. x Competition"
 )

row.names(coef_p_ars) <- term_names
row.names(coef_p_ows) <- term_names
row.names(coef_p_kpd) <- term_names

names(coef_p_ars) <- c("Estimate", "SE", "Z", "P", "Est ± se")
names(coef_p_ows) <- c("Estimate", "SE", "Z", "P", "Est ± se")
names(coef_p_kpd) <- c("Estimate", "SE", "Z", "P", "Est ± se")
```

### Nonlinear results
The effect of competition on linear and nonlinear selection on female behavioral traits for annual reproductive success. Posterior modes are given with highest posterior density intervals in parentheses.

#### ARS
```{r coef_p_ars, results='asis'}
pandoc.table(coef_p_ars[c(1,3,2,4:16), c(5,3,4)],
 split.tables = 160)
```

#### OWS
```{r coef_p_ows, results='asis'}
pandoc.table(coef_p_ows[c(1,3,2,4:16), c(5,3,4)],
 split.tables = 160)
```

#### Fecundity
```{r coef_p_kpd, results='asis'}
pandoc.table(coef_p_kpd[c(1,3,2,4:16), c(5,3,4)],
 split.tables = 160)
```

#### Plot of quadratic interaction
```{r figures_blups, tidy=TRUE, tidy.opts=list(keep.blank.line=TRUE, width.cutoff=60)}
library(effects)
library(ggplot2)

g.ows <- glm(prop ~ aggression_s*competition_s + activity_s*competition_s + 
  docility_s*competition_s + aggression_s:activity_s*competition_s + 
  I(aggression_s^2)*competition_s,
  data = filter(fit_raneff_data, type == "blup"),
  weights = kprod, family = binomial)
e.ows <- effect(term ="aggression_s:competition_s:activity_s", mod = g.ows)

e <- Effect(c("aggression_s", "activity_s", "competition_s"), g.ows,
  xlevels = list(aggression_s = 100, activity_s = 2, competition_s = 2))

s <- summary(e, type = "link")
se <- s$effect
su <- s$upper
sl <- s$lower
d <- as.data.frame(se)
du <- as.data.frame(su)
dl <- as.data.frame(sl)
names(d) <- c("la.lc", "ha.lc", "la.hc", "ha.hc")
names(du) <- c("la.lc", "ha.lc", "la.hc", "ha.hc")
names(dl) <- c("la.lc", "ha.lc", "la.hc", "ha.hc")

plot_d <- data.frame(
	Aggression = as.numeric(rep(row.names(s$effect), 12)),
	OWS = c(d$la.lc, d$ha.lc, d$la.hc, d$ha.hc, du$la.lc, du$ha.lc, du$la.hc,
    du$ha.hc, dl$la.lc, dl$ha.lc, dl$la.hc, dl$ha.hc),
	Competition = rep(rep(c("Low\nCompetition", "High\nCompetition"),
    each = 200), 3),
	Activity = rep(rep(c("Low", "High"), each = 100), 6),
	type = rep(c("main", "upper", "lower"), each = 400)
)
plot_d$env <- paste(plot_d$Competition, plot_d$Activity, sep = ".")

quad_plot <- ggplot(plot_d, aes(x = Aggression, y = OWS)) + geom_line(aes(alpha = Activity, linetype = type, size = type)) +  facet_wrap( ~ Competition) + scale_alpha_discrete(range = c(1,0.3)) + scale_linetype_manual(values = c(2,1,2)) + scale_size_manual(values = c(0.3,1,0.3)) + ylab("Offspring\nOverwinter Survival") + xlab("Aggression") + theme_bw(base_size = 10) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_rect(linetype = "solid", colour = "black"), axis.ticks = element_blank(), axis.text = element_text(size = 10), legend.key=element_blank(), strip.background = element_blank()) + guides(linetype = FALSE, size = FALSE, alpha = guide_legend(override.aes=list(size = 1))) + theme(legend.position = c(0.75, 0.25), legend.background = element_blank(), legend.key.size = unit(0.4, "cm")) + theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

pdf("figure/quad_plot.pdf", width = 3.14, height = 2)
quad_plot
dev.off()

```
```{r fig.width=3.14, fig.height=2}
quad_plot
```

#### Tile plot of interaction
```{r tile_plot, tidy=TRUE, tidy.opts=list(keep.blank.line=TRUE, width.cutoff=60)}

n = 12
e <- Effect(c("aggression_s", "activity_s", "competition_s"), g.ows,
  xlevels = list(aggression_s = n, activity_s = n, competition_s = 2))
s <- summary(e, type = "response")
de <- as.data.frame(s$effect)
de_lc <- de[ ,1:n]
de_hc <- de[ ,(n+1):(2*n)]

fix.names <- function(x){
	a <- unlist(lapply(strsplit(names(x), split = "\\."), "[[", 1))
	b <- unlist(lapply(strsplit(names(x), split = "\\."), "[[", 2))
	out <- paste(a,b, sep = ".")
	return(out)
	}

d_hc <- data.frame(Aggression = rep(row.names(de_hc), n),
  Activity = rep(fix.names(de_hc), each = n), OWS = as.vector(as.matrix(de_hc)))
d_hc$Aggression <- as.numeric(as.character(d_hc$Aggression))
d_hc$Activity   <- as.numeric(as.character(d_hc$Activity))

d_lc <- data.frame(Aggression = rep(row.names(de_lc), n),
  Activity = rep(fix.names(de_lc), each = n), OWS = as.vector(as.matrix(de_lc)))
d_lc$Aggression <- as.numeric(as.character(d_lc$Aggression))
d_lc$Activity   <- as.numeric(as.character(d_lc$Activity))

tile_plot <- ggplot(d_lc, aes(x = Aggression, y = Activity, z = OWS)) +  geom_tile(aes(alpha = OWS), fill = "black", size = 0) + scale_alpha_continuous(range=c(1,0)) + ylab("Activity") + xlab("Aggression") + theme_bw(base_size = 10) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_rect(linetype = "solid", colour = "black"), axis.ticks = element_blank(), legend.key=element_blank(),strip.background = element_blank()) + guides(linetype = FALSE, size = FALSE, alpha = FALSE)+ theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

pdf("figure/tile.pdf", width = 3.14, height = 3.14)
tile_plot
dev.off()
```

```{r fig.width=3.14, fig.height=3.14}
tile_plot
```