<!--pandoc
t: html
default-image-extension: png
template: templates/html.template
toc-depth: 4
toc:

t: latex
s:
S:
latex-engine: xelatex
template: templates/latex.template
default-image-extension: pdf
toc-depth: 4
toc:
-->

```{r echo=FALSE, cache=FALSE, results="hide"}
opts_chunk$set(echo = FALSE, fig.cap='', dev=c('png', 'pdf'), fig.width=6,
  fig.height=4, results='asis', cache=FALSE, message=FALSE)
opts_knit$set('upload.fun' = function(x) sub("\\.[[:alnum:]]*$", "", x) )
```

# Supplementary Material
Supplementary material for:

R. W. Taylor, M. M. Humphries, S. Boutin, J. C. Gorrell, D. W. Coltman, and A. G. McAdam. Selection on female behaviour fluctuates with offspring environment. Journal of Evolutionary Biology, 2014.



Data and code used in the analyses are available on github

    https://github.com/rwtaylor/2014-female-selection

and archived on Zenodo

    http://dx.doi.org/10.5281/zenodo.10908


```{r load_packages, cache=FALSE, results='hide'}
library(MASS) # MASS clashes with dplyr... so always load first
library(pander) # pander clashes with dplyr... so always load first
set.alignment('right', row.names = 'left')
panderOptions('table.split.table', Inf)
library(dplyr)
library(MCMCglmm)
```
## Table S1
```{r s1}
load("mcmc_repeatability_summary.RData")
table_summary <- as.matrix(table_summary)
dimnames(table_summary)[[2]] <- c("Behavior", "Overall Repeatability", "Repeatability Within Years", "Repeatability Across Years")
pandoc.table(table_summary, caption = "Repeatability within and across years. Repeatabilities were estimated using linear mixed effects models with individual as a random effect. Repeatability across years was estimated after randomly sampling, for each individual, only one behavioural measure per year.")
```

## Table S2
```{r s2}
fitness <- read.table(file = "data/fitness+competition.csv", sep = ',',
  header = TRUE, stringsAsFactors = FALSE)
fitness <- tbl_df(fitness)
fit_table <- fitness %>% group_by(Grid, Year, add = FALSE) %>% summarise(tot_kprod = sum(kprod), tot_ars = sum(ars_all), competition = round(mean(competition), digits = 2))
fit_table <- as.matrix(fit_table)
dimnames(fit_table)[[2]] <- c("Study Area", "Year", "N juveniles", "N survive", "Competition")
pandoc.table(fit_table, caption = "Variation in competition across years and study areas. N juveniles is the number of juveniles produced in the study area. N survive is the number of juveniles that recruited into the population by surviving overwinter to the next spring. Competition is the ratio of juveniles produced to juveniles recruited.")
```

## Table S3
```{r s3}
load("data/analyses_data/ars_year.RData")
# Test fit of models. Does the addition of year:traits improve the fit?
library(car)
library(lme4)
aod <- Anova(ars_year, type = 2)
aod <- data.frame(aod)
aod$Chisq <- round(aod$Chisq ,digits = 2)

# Function to convert small p-values into 'P < X'
p.format <- function(x){ 
	out <- signif(x, digits = 2)
  out[x < 0.005]  <- "< 0.005"
	out[x < 0.001]  <- "< 0.001"
	out[x < 0.0001] <- "< 0.0001"
	return(out)
}
# Format p values
aod[ ,3] <- p.format(aod[ ,3])
row.names(aod) <- c("Year", "Grid", "Activity", "Aggression", "Docility",
  "Year x Activity", "Year x Aggression", "Year x Docility")
set.alignment('right', row.names = 'left')
pandoc.table(aod, caption = 
  "Generalized linear mixed model results showing the interactions between year and the behavioural traits (BLUPs). Significance was calculated with Wald tests from an analysis of deviance. GLMMs were fitted with squirrel identity as a random effect and assumed a Poisson error distribution.")
```

## Table S4
```{r s4}
load("data/analyses_data/sel_grads_mcmc.RData")
load("data/analyses_data/fit_raneff_data.RData")

N <- fit_raneff_data %>%
  filter(type == "blup") %>%
  group_by(Year, add = FALSE) %>%
  summarise(n(), doc_mean = mean(docility, na.rm = TRUE))

# Format for table
sgt <- sel_grads_mcmc
sgt$sig_star <- ""
sgt$sig_star[sgt$post_mode > 0 & sgt$lower > 0] <- "*"
sgt$sig_star[sgt$post_mode < 0 & sgt$upper < 0] <- "*"
sgt$post_mode <- format(round(sgt$post_mode, digits = 2), digits = 1,
  nsmall = 2)
sgt$lower     <- format(round(sgt$lower,     digits = 2), digits = 1,
  nsmall = 2)
sgt$upper     <- format(round(sgt$upper,     digits = 2), digits = 1,
  nsmall = 2)
sgt$coef      <- paste(sgt$post_mode, " (", sgt$lower, " to ", sgt$upper,")",
  sgt$sig_star, sep = '')

sgt_agg <- filter(sgt, variable == "Aggression", standardization == "None")
sgt_act <- filter(sgt, variable == "Activity",   standardization == "None")
sgt_doc <- filter(sgt, variable == "Docility",   standardization == "None")

sgt_agg_sd <- filter(sgt, variable == "Aggression", standardization == "SD")
sgt_act_sd <- filter(sgt, variable == "Activity",   standardization == "SD")
sgt_doc_sd <- filter(sgt, variable == "Docility",   standardization == "SD")


doc_post_mode <- sel_grads_mcmc %>% filter(standardization == "None" & variable == "Docility") 
doc_post_mode$post_mode_m <- doc_post_mode$post_mode * N$doc_mean
doc_post_mode$post_mode_m <- format(round(doc_post_mode$post_mode_m, digits = 2), digits = 1, nsmall = 2)

pandoc.table(
  data.frame(Year = N$Year, N = N[ ,2], Aggression = sgt_agg$coef,
    Acitivity = sgt_act$coef, Docility = sgt_doc$coef
  ),
  caption = "Non-standardized linear selection gradients (β′) for female behavioural traits through annual reproductive success after accounting for behavioural measurement uncertainty (see methods for details). Posterior modes are given with the lower and upper bounds of the 0.95 highest posterior density interval. "
  )
```
## Table S5
```{r s5}
pandoc.table(
  data.frame(Year = N$Year, N = N[ ,2], Aggression = sgt_agg_sd$coef,
    Acitivity = sgt_act_sd$coef, Docility = sgt_doc_sd$coef
  ),
  caption = "SD-standardized linear selection gradients (β′) for female behavioural traits through annual reproductive success after accounting for behavioural measurement uncertainty (see methods for details). Posterior modes are given with the lower and upper bounds of the 0.95 highest posterior density interval. "
  )
```

## Table S6
```{r s6}
pandoc.table(
  data.frame(Year = N$Year, N = N[ ,2], Mean_docility = N$doc_mean, Mean_stan_B = doc_post_mode$post_mode_m
  ),
  caption = "Mean-standardized linear selection gradients (β′) for female docility through annual reproductive success after accounting for behavioural measurement uncertainty (see methods for details). Posterior modes are given with the lower and upper bounds of the 0.95 highest posterior density interval. Activity and aggression are synthetic behavioural measures, with means of zero and so can not be mean standardized."
  )
```

## Table S7
```{r s7}
load("data/analyses_data/sel_grads_blup.RData")
# Format for table
sgt <- sel_grads_blup
sgt$sig_star <- ""
sgt$sig_star[sgt$coefficients > 0 & sgt$lower > 0] <- "*"
sgt$sig_star[sgt$coefficients < 0 & sgt$upper < 0] <- "*"
sgt$coefficients <- format(round(sgt$coefficients, digits = 2),
  digits = 1, nsmall = 2)
sgt$lower <- format(round(sgt$lower, digits = 2),
  digits = 1, nsmall = 2)
sgt$upper <- format(round(sgt$upper, digits = 2),
  digits = 1, nsmall = 2)
sgt$prb <- NA
sgt$coef <- paste(sgt$coefficients,
  " (", sgt$lower, " to ", sgt$upper,")", sgt$sig_star, sep = '')

sgt_agg <- filter(sgt, standardization == "None" & variable == "Aggression")
sgt_act <- filter(sgt, standardization == "None" & variable == "Activity")
sgt_doc <- filter(sgt, standardization == "None" & variable == "Docility")

sgt_agg_sd <- filter(sgt, standardization == "SD" &  variable == "Aggression")
sgt_act_sd <- filter(sgt, standardization == "SD" &  variable == "Activity")
sgt_doc_sd <- filter(sgt, standardization == "SD" &  variable == "Docility")

sgt_doc_ms <- filter(sgt, standardization == "Mean" &  variable == "Docility")

N <- fit_raneff_data %>%
  filter(type == "blup") %>%
  group_by(Year, add = FALSE) %>%
  summarise(n = n(), t_kprod = sum(kprod), t_ars = sum(ars_all), mean_docil = mean(docility, na.rm = TRUE))

pandoc.table(
  data.frame(
    Year = N$Year,
    Aggression = sgt_agg$coef,
    Activity = sgt_act$coef,
    Docility = sgt_doc$coef
  ),
  caption ="Non-standardized linear selection gradients (β′) ± standard errors for female behavioural traits through annual reproductive success. Selection gradients were estimated from single realized BLUPs of behavioural traits. Significance was assessed using the sim() function in the R package arm."
)
```

## Table S8
```{r s8}
pandoc.table(
  data.frame(
    Year = N$Year,
    Docility = sgt_doc_ms$coefficients,
    mean = N$mean_docil
  ),
  caption ="Mean-standardized linear selection gradients (β′) ± standard errors for female docility. Selection gradients were estimated from single realized BLUPs of behavioural traits. Significance was assessed using the sim() function in the R package arm. Activity and aggression are synthetic behavioural measures, with means of zero and so can not be mean standardized."
)

```

## Table S9
```{r s9}
getPosteriorParams <- function(x){
  require(MCMCglmm)
  dat_mcmc <- mcmc(x)
  pm <- posterior.mode(dat_mcmc)
  hpd <- HPDinterval(dat_mcmc, prob = 0.9)
  pm_table <-  format(round(pm , digits = 2), digits = 1, nsmall = 2,
    scientific = FALSE)
  hpd_table <- format(round(hpd, digits = 2), digits = 1, nsmall = 2,
    scientific = FALSE)
  pm_hpd_table <- data.frame(cbind(pm_table, hpd_table))
  pm_hpd_table$pm_hpd <- paste(
    pm_table, " (", hpd_table[ ,1], ", ", hpd_table[ ,2], ")", sep = ''
    )
  pm_hpd_table$sig[sign(hpd[ ,1]) == sign(hpd[ ,2])] <- "*"
  pm_hpd_table$sig[sign(hpd[ ,1]) != sign(hpd[ ,2])] <- " "
  pm_hpd_table$space[sign(hpd[ ,1]) == sign(hpd[ ,2])] <- "*"
  pm_hpd_table$space[sign(hpd[ ,1]) != sign(hpd[ ,2])] <- "&nbsp;"
  pm_hpd_table$pm_hpd <- paste(pm_hpd_table$pm_hpd, pm_hpd_table$sig, sep = "")
  return(pm_hpd_table)
}

load("data/analyses_data/nonlinear_mcmc_models.RData")

pm_hpd_ars <- getPosteriorParams(
  nonlinear_mcmc[nonlinear_mcmc$fitness =="ars", 3:18])
pm_hpd_ows <- getPosteriorParams(
  nonlinear_mcmc[nonlinear_mcmc$fitness =="ows", 3:18])
pm_hpd_kpd <- getPosteriorParams(
  nonlinear_mcmc[nonlinear_mcmc$fitness =="kpd", 3:18])

nonlinear_results_mcmc <- data.frame(ARS = pm_hpd_ars$pm_hpd,
  OWS = pm_hpd_ows$pm_hpd, Fecundity = pm_hpd_kpd$pm_hpd)
  
row.names(nonlinear_results_mcmc) <- c("Intercept", "Aggression",
 "Competition", "Activity", "Docility", "Aggression^2", "Activity^2",
 "Docility^2", "Aggression x Competition", "Activity x Competition",
 "Docility x Competition", "Aggression x Activity",
 "Aggression^2 x Competition", "Activity^2 x Competition",
 "Docility^2 x Competition", "Agg. x Act. x Competition"
 )
pandoc.table(nonlinear_results_mcmc[c(1,3,2,4:16), ], 
 split.tables = 160, caption = "Selection on female aggression and docility, through annual reproductive success, interacted significantly with juvenile offspring competition for vacant territories after accounting for behavioural measurement uncertainty. The generalized linear mixed model for annual reproductive success assumed a Poisson error distribution, while the model for offspring overwinter survival assumed a binomial error distribution weighted by fecundity. Random effects for identity and grid-year were included in both models to account for pseudoreplication. Presented are posterior modes of the distribution of coefficients from 1000 models of 1000 sets of individual random effects of each behavioural trait generated with MCMCglmm.")
```

## Table S10
```{r s10}
load("data/analyses_data/nl.blup_models.RData")

coef_p_ars <- getLmerParams(ars_nl_model)
coef_p_ows <- getLmerParams(ows_nl_model)
coef_p_kpd <- getLmerParams(kpd_nl_model)

term_names <- c("Intercept", "Aggression",
 "Competition", "Activity", "Docility", "Aggression^2", "Activity^2",
 "Docility^2", "Aggression x Competition", "Activity x Competition",
 "Docility x Competition", "Aggression x Activity",
 "Aggression^2 x Competition", "Activity^2 x Competition",
 "Docility^2 x Competition", "Agg. x Act. x Competition"
 )

row.names(coef_p_ars) <- term_names
row.names(coef_p_ows) <- term_names
row.names(coef_p_kpd) <- term_names

names(coef_p_ars) <- c("Estimate", "SE", "Z", "P", "Est ± se")
names(coef_p_ows) <- c("Estimate", "SE", "Z", "P", "Est ± se")
names(coef_p_kpd) <- c("Estimate", "SE", "Z", "P", "Est ± se")

pandoc.table(coef_p_kpd[c(1,3,2,4:16), c(5,3,4)],
 split.tables = 160, caption = "There was no evidence for selection on female behaviour through fecundity. Results from a generalized linear mixed model of fecundity with individual and grid-year as random effects. The model was fitted with a Poisson error distribution. This model ignores uncertainty around the BLUPs used for each indivdiual's behavioral measure.")
```

## Figure S1

![](final_figures/F6) 

High activity females (black lines) were favoured when they were also aggressive in high competition environments (left panel). But, for low activity females, there was stabilizing selection for low to moderate levels of aggression through offspring overwinter survival (b = –3.11 ± 1.36, Z = –2.29, P = 0.02). This positive correlational selection was not present in low competition environments (right panel). The interaction between aggression, activity and competition was significant for offspring overwinter survival (b = 3.95 ± 1.86, Z = 2.13, P = 0.03). Predicted values from the model for offspring overwinter survival (Table 3) were plotted for the highest and lowest values of competition we measured. Dashed lines represent 95% confidence intervals around the predicted values.

## Figure S2

![](final_figures/F5) 

The predicted relative fitness surface, as a function of female aggression and activity, was saddle shaped when competition among juveniles for vacant territories was high. Darker squares correspond to higher fitness. Fitness peaks (+) occurred for females with high aggression and activity, and for females with low-moderate aggression and low activity. Predicted values from a linear model of relative fitness with the same predictors as the models in Table 3, were plotted for the highest levels of competition measured and mean docility.